---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# peacock

<!-- badges: start -->
[![R-CMD-check](https://github.com/samuelbharti/peacock/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/samuelbharti/peacock/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

peacock helps you quickly set up new R projects with pre-configured directory structures and files. Stop creating the same folders and files manually every time you start a project. Just run a function and get working.

## Why peacock?

When starting a new project, you probably find yourself:

- Creating the same folders over and over (data, scripts, outputs)
- Setting up Shiny apps with the same basic structure
- Writing boilerplate code for UI, server, and global files
- Manually organizing files for reproducible research

peacock automates this. It gives you clean, organized project templates so you can start coding immediately.

## Installation

Install from GitHub:

``` r
# install.packages("devtools")
devtools::install_github("samuelbharti/peacock")
```

## What can peacock do?

### 1. Initialize a Shiny app structure

Creates a complete Shiny app with organized folders and starter files.

```{r example, eval = FALSE}
library(peacock)

# Set up a new Shiny project
init_shiny(path = "my_shiny_app")
```

This creates:
- `ui.R`, `server.R`, `global.R` - Your main Shiny files
- `modules/` - For modular Shiny components
- `userInterface/` - UI components organized separately
- `www/` - Static files (CSS, images, JavaScript)
- `data/`, `R/`, `dev/` - Standard project folders
- `Dockerfile` - Ready for containerization
- `.gitignore` and `.Renviron` - Project configuration

### 2. Create a changelog

Track project changes in a structured markdown file.

```{r eval = FALSE}
init_changelog_md(path = "my_project")
```

Creates a `CHANGELOG.md` file with a simple format for documenting your work.

### 3. Use GitHub templates

Pull down complete project templates from GitHub. Use a built-in name, or **any**
GitHub repository as `"owner/repo"` (optionally pinned with `"owner/repo@ref"`).

```{r eval = FALSE}
# Built-in templates
init_template("shiny", path = "my_project")
init_template("cgds", path = "research_project")

# Any GitHub repo, optionally pinned to a branch, tag, or commit
init_template("owner/repo", path = "my_project")
init_template("owner/repo@dev", path = "my_project")

# See the built-in templates
peacock_templates()
```

### 4. Set up tool review projects

Organize projects that compare multiple tools or methods.

```{r eval = FALSE}
tool_review_template(
  tool_name = c("tool1", "tool2", "tool3"),
  tool_url = c("https://tool1.com", "https://tool2.com", "https://tool3.com"),
  path = "tool_comparison"
)
```

This creates organized folders for data, scripts, outputs, and documentation for each tool.

### 5. Scaffold a reproducible analysis project

Set up a tidy layout for a data-analysis or research project.

```{r eval = FALSE}
init_analysis(path = "my_study")
```

Creates `data/{raw,processed}`, `R/`, `analysis/` (with a starter Quarto notebook),
and `output/{figures,tables}`, plus a README and `.gitignore`.

### 6. Scaffold a Quarto project

Create a Quarto website, book, or manuscript.

```{r eval = FALSE}
init_quarto(path = "my_site", type = "website")
```

`type` can be `"website"` (default), `"book"`, or `"manuscript"`; each gets a
`_quarto.yml` and starter documents.

### 7. Scaffold a Python project

peacock stays an R package, but it can emit a Python project too.

```{r eval = FALSE}
init_python(path = "my_pkg")
```

Creates a src-layout package with `pyproject.toml` (ruff + pytest), a starter
module and test, `.gitignore`, and `AGENTS.md`.

### Every project is AI-ready

`init_shiny()`, `init_analysis()`, `init_quarto()`, and `init_python()` also drop an `AGENTS.md`
(plus a `CLAUDE.md` that imports it) describing how to run, build, and work in the
project — so AI coding assistants are productive from the first commit.

## Quick start

```{r eval = FALSE}
library(peacock)

# Create a new Shiny app in the current directory
init_shiny()

# Or specify a path
init_shiny(path = "path/to/new/project", confirm = FALSE)
```

Set `confirm = FALSE` to skip the confirmation prompt (useful for scripting).

## Learn more

- Full documentation: http://www.samuelbharti.com/peacock/
- Issues and feedback: https://github.com/samuelbharti/peacock/issues

## License

GPL-3

